Sparse Function-space Representation of Neural Networks

### 2023-09-05 workshops/icml-duality/main.tex
shortened to fit in 4 pages on arxiv
retaining to maintaining

\begin{abstract}
Deep neural networks (NNs) are known to lack uncertainty estimates and struggle to incorporate new data. We present a method that mitigates these issues by converting NNs from weight space to function space, via a dual parameterization. Importantly, the dual parameterization enables us to formulate a sparse representation that captures information from the entire data set. This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance. We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchmark tasks.
\end{abstract}

@@

% We first compare \our to other posthoc Bayesian deep learning approaches.
% In particular, we compare to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM).
We first compare \our to the Laplace approximation when making predictions with {\em (i)}~the nonlinear NN (BNN) and {\em (ii)}~the generalised linear model (GLM) in \cref{eq-glm}.
We use the Laplace PyTorch library \citep{daxberger2021laplace} with the full Hessian. %, i.e. we do not resort to the diagonal or KFAC approximations.
It is common practice to tune the prior precision $\delta$ after training the NN.
That is, find a prior precision $\delta_{\text{tune}}$ which has a better NLPD on the validation set than the $\delta$ used to train the NN.
Note that this leads to a different prior precision being used for training and inference.
We highlighted that technically this invalidates the Laplace/SFR methods as the NN weights are no longer the MAP weights.
Nevertheless, we report results when the prior precision $\delta$ is tuned (\cref{tbl:uci} right) and is not tuned (\cref{tbl:uci} left).
When tuning the prior precision $\delta$, \our matches the performance of the Laplace methods (BNN/GLM).
Interestingly, \our also  performs well without tuning the prior precision $\delta$, unlike the Laplace methods (BNN/GLM).

>>>>

\begin{abstract}
Deep neural networks (NNs) are known to lack uncertainty estimates and struggle to incorporate new data. We present a method that mitigates these issues by converting NNs from weight space to function space, via a dual parameterization. Importantly, the dual parameterization enables us to formulate a sparse representation that captures information from the entire data set. This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst maintaining predictive performance. We provide proof-of-concept demonstrations with the proposed approach for quantifying uncertainty in supervised learning on UCI benchmark tasks.
\end{abstract}

@@

% We first compare \our to other posthoc Bayesian deep learning approaches.
% In particular, we compare to the Laplace approximation when making predictions with 1) the nonlinear NN (BNN) and 2) the generalised linear model (GLM).
We first compare \our to the Laplace approximation when making predictions with {\em (i)}~the nonlinear NN (BNN) and {\em (ii)}~the generalised linear model (GLM) in \cref{eq-glm}.
We use the Laplace PyTorch library \citep{daxberger2021laplace} with the full Hessian. %, i.e. we do not resort to the diagonal or KFAC approximations.
It is common practice to tune the prior precision $\delta$ after training the NN.
That is, find a prior precision $\delta_{\text{tune}}$ which has a better NLPD on the validation set than the $\delta$ used to train the NN.
Note that this leads to a different prior precision being used for training and inference.
We highlighted that technically this invalidates the Laplace/SFR methods as the NN weights are no longer the MAP weights.
Nevertheless, we report results when the prior precision $\delta$ is tuned (\cref{tbl:uci} right) and is not tuned (\cref{tbl:uci} left).
When tuning the prior precision $\delta$, \our matches the performance of the Laplace methods (BNN/GLM).
Interestingly, \our also  performs well without tuning the prior precision $\delta$, unlike the Laplace methods.
